\Large{All in the family:\\German twin finishing times in\\the 2016 women's Olympic marathon}

### 2017-02-24 paper/paper.tex
a couple changes

From our simulations we generate intervals which describe the extent
of the variability in marathon finishing times. For example, in 95\%
of the simulations in which Anna Hahner completed the marathon, her
finishing time was between 8,369 seconds and 9,999 seconds. This is
consistent with Anna's observed finishing time in Rio, which was 9,932
seconds. In fact, our simulations estimate that Anna should have
finished the Rio marathon in 9,181 seconds, which is slightly more
than 12 minutes faster than her actual time. Lisa Hahner's
corresponding 95\% interval is 8,507 to 10,143 with an observed
finishing time of 9,933 seconds.

>>>>

From our simulations we generate intervals which describe the extent
of the variability in marathon finishing times. For example, in 95\%
of the simulations in which Anna Hahner completed the marathon, her
finishing time was between 8,369 seconds and 9,999 seconds. This is
consistent with Anna's observed finishing time in Rio, which was 9,932
seconds. Nonetheless, her finishing time was on the slower end of this interval,.   
In fact, our simulations estimate that, given Anna's personal best marathon time
and her age, she would be expected to finish the Rio marathon in 9,181 seconds, which is slightly more
than 12 minutes faster than her actual time.  This is similar to her sister's result. Lisa Hahner's
corresponding 95\% interval is 8,507 to 10,143 with a mean of 9,319.  Her observed
finishing time of 9,933 seconds.
